---
title: "Happy Moments"
output: html_document
date: "2024-01-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Install packages
```{r, warning=FALSE, message=FALSE,echo=FALSE}
if (!require("tidyverse")) install.packages("tidyverse")
if (!require("tidytext")) install.packages("tidytext")
if (!require("DT")) install.packages("DT")
if (!require("tibble")) install.packages("tibble")
if (!require("rCharts")) install.packages("rCharts")
if (!require("htmlwidgets")) install.packages("htmlwidgets")
if (!require("tm")) install.packages("tm")
if (!require("broom")) install.packages("broom")
if (!require("wordcloud")) install.packages("wordcloud")
if (!require("RColorBrewer")) install.packages("RColorBrewer")
if (!require("ggwordcloud")) install.packages("ggwordcloud")
```

Install additional packages
```{r, warning=FALSE, message=FALSE,echo=FALSE}
if (!require("devtools")) install.packages("devtools")
devtools::install_github("ramnathv/rCharts")
```

Load packages 
```{r, warning=FALSE, message=FALSE,echo=FALSE}
library(tidyverse)   
library(tidytext)     
library(DT)           
library(tibble)       
library(rCharts)      
library(htmlwidgets) 
library(ggplot2)
library(tm)
library(broom)
library(dplyr)
library(wordcloud)
library(RColorBrewer)
library(stringr)
library(ggwordcloud)
```


Read files
```{r, warning=FALSE, message=FALSE,echo=FALSE}
cleaned_hm <- read.csv("E:/GR 5243/HappyDB/happydb/data/cleaned_hm.CSV")
head(cleaned_hm)

demographic <- read.csv("E:/GR 5243/HappyDB/happydb/data/demographic.CSV")
head(demographic)

original_hm <- read.csv("E:/GR 5243/HappyDB/happydb/data/original_hm.CSV")
head(original_hm)

senselabel <- read.csv("E:/GR 5243/HappyDB/happydb/data/senselabel.CSV")
head(senselabel)

merged_df <- inner_join(cleaned_hm, demographic, by = "wid")
```

Missing Values
```{r missing values, warning=FALSE, message=FALSE,echo=FALSE}
merged_modified <- merged_df %>%
  na.omit()
df <- merged_modified %>% 
  select(-hmid, -wid, -original_hm, -modified,
         -num_sentence, -ground_truth_category,
         -parenthood, -reflection_period)


df$gender[df$gender == ""] <- NA
df <- na.omit(df)

df$gender[df$country == ""] <- NA
df <- na.omit(df)
```

Data Exploration
Differences in the types of exercise in happy moments between genders
```{r, warning=FALSE, message=FALSE,echo=FALSE}
exercise_df <- df %>%
  filter(predicted_category == "exercise")
write.csv(exercise_df, file = "E:/GR 5243/Spring2024-TZStatsADS-YangYu-proj/out/processed_moments.csv", row.names = FALSE)


exercise_count <- exercise_df %>%
  count(gender, predicted_category)

p <- ggplot(exercise_count, aes(x = gender, y = n, fill = gender)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  facet_wrap(~predicted_category, scales = "free_y") + 
  theme_minimal() +
  labs(title = "Differences in the Types of Exercise in Happy Moments Between Genders",
       x = "Gender", 
       y = "Count of Exercise-related Happy Moments",
       fill = "Gender")
ggsave("plot.png", plot = p, width = 10, height = 6, dpi = 300)
```

Preliminary cleaning of text
We clean the text by  removing punctuation, numbers, empty words and extra white space.
```{r text preprocess, warning=FALSE, message=FALSE,echo=FALSE}
df1 <- df
clean_text <- function(text) {
  text <- gsub("\\b[0-9]+\\b", "", text) 
  text <- gsub("[0-9]+\\.[0-9]+", "", text) 
  text <- gsub("\\b[0-9]+[A-Za-z0-9]+\\b", "", text) 
  text <- gsub("[^A-Za-z' ]", "", text)
  text <- gsub("\\s+", " ", text)
  text <- trimws(text)
  
  return(text)
}

df1$cleaned_hm <- sapply(df1$cleaned_hm, clean_text)


cat(df1$cleaned_hm[1:10], sep = "\n") 

df2 <- df1
df3 <- df1

```

Text Data Analysis
1.Stop Words and Word Cloud
```{r word cloud, warning=FALSE, message=FALSE,echo=FALSE}
df_exercise <- df1 %>%
  filter(predicted_category == "exercise")

df_female <- df_exercise %>% filter(gender == "f")
df_male <- df_exercise %>% filter(gender == "m")
df_other <- df_exercise %>% filter(gender == "o")

print(df_female)
print(df_male)
print(df_other)

df_female1 <- df_female
df_male1 <- df_male
df_other1 <- df_other

```


(1)Female
```{r female, warning=FALSE, message=FALSE,echo=FALSE}
data_stop_words <-  stop_words
df_female1_clean <- df_female1 %>%
  unnest_tokens(word, cleaned_hm) %>%
  anti_join(data_stop_words)

word_freq_female <- df_female1_clean %>%
  count(word, sort = TRUE)

set.seed(1234) 
wordcloud_female <- wordcloud(words = word_freq_female$word, freq = word_freq_female$n, min.freq = 1,
          max.words = 100, random.order = FALSE, rot.per = 0.35,
          colors = brewer.pal(8, "Dark2"))

png("wordcloud_female.png", width = 1280, height = 800)
wordcloud(words = word_freq_female$word, freq = word_freq_female$n, min.freq = 1,
          max.words = 100, random.order = FALSE, rot.per = 0.35, colors = brewer.pal(8, "Dark2"))
dev.off()
```

(2)Male
```{r male, warning=FALSE, message=FALSE,echo=FALSE}
data_stop_words <-  stop_words
df_male1_clean <- df_male1 %>%
  unnest_tokens(word, cleaned_hm) %>%
  anti_join(data_stop_words)

word_freq_male <- df_male1_clean %>%
  count(word, sort = TRUE)

set.seed(1234) 
wordcloud_male <- wordcloud(words = word_freq_male$word, freq = word_freq_male$n, min.freq = 1,
          max.words = 100, random.order = FALSE, rot.per = 0.35,
          colors = brewer.pal(8, "Dark2"))
png("wordcloud_male.png", width = 1280, height = 800)
wordcloud(words = word_freq_male$word, freq = word_freq_male$n, min.freq = 1,
          max.words = 100, random.order = FALSE, rot.per = 0.35, colors = brewer.pal(8, "Dark2"))
dev.off()

```

(3)Other
```{r other, warning=FALSE, message=FALSE,echo=FALSE}
data_stop_words <-  stop_words
df_other1_clean <- df_other1 %>%
  unnest_tokens(word, cleaned_hm) %>%
  anti_join(data_stop_words)

word_freq_other <- df_other1_clean %>%
  count(word, sort = TRUE)

set.seed(1234) 
wordcloud_other <- wordcloud(words = word_freq_other$word, freq = word_freq_other$n, min.freq = 1,
          max.words = 100, random.order = FALSE, rot.per = 0.35,
          colors = brewer.pal(8, "Dark2"))

png("wordcloud_other.png", width = 1280, height = 800)
wordcloud(words = word_freq_other$word, freq = word_freq_other$n, min.freq = 1,
          max.words = 100, random.order = FALSE, rot.per = 0.35, colors = brewer.pal(8, "Dark2"))
dev.off()

```

2. Frequency Words and Its Sentences
(1)Female
```{r female frequency,  warning=FALSE, message=FALSE,echo=FALSE}
top_words_female <- head(word_freq_female$word, 3)

original_sentences_female <- df_female1 %>%
  filter(grepl(paste(top_words_female, collapse="|"), cleaned_hm)) %>%
  .$cleaned_hm

head(original_sentences_female)





```
Among the high-frequency words in our findings for moments that make women feel happy in their exercise are "gym", "workout", and "run". We also matched the original sentences in which the words were found.

(2)Male
```{r male frequency,  warning=FALSE, message=FALSE,echo=FALSE}
top_words_male <- head(word_freq_male$word, 3)

original_sentences_male <- df_male1 %>%
  filter(grepl(paste(top_words_male, collapse="|"), cleaned_hm)) %>%
  .$cleaned_hm

head(original_sentences_male)
```
Among the high-frequency words in our findings for moments that make men feel happy in their exercise are "gym", "workout", and "run". We also matched the original sentences in which the words were found.

(3)Other
```{r other frequency,  warning=FALSE, message=FALSE,echo=FALSE}
top_words_other <- head(word_freq_other$word, 3)

original_sentences_other <- df_other1 %>%
  filter(grepl(paste(top_words_other, collapse="|"), cleaned_hm)) %>%
  .$cleaned_hm

head(original_sentences_other)
```
Among the high-frequency words in our findings for moments that make other feel happy in their exercise are "gym", "night", and "time". We also matched the original sentences in which the words were found.





References

Asai, A., Evensen, S., Golshan, B., Halevy, A., Li, V., Lopatenko, A., Stepanov, D., 
Suhara, Y., Tan, W.-C., Xu, Y. (2018). "HappyDB: A Corpus of 100,000 Crowdsourced 
Happy Moments", LREC '18, May. (to appear)

